---
title: "Seal cleaning"
author: "Ian Hoppe"
date: "`r format( Sys.Date(), '%B %d, %Y' )`"
output:
  bookdown::html_document2:
    theme: lumen
    highlight: tango
    number_sections: FALSE
---

```{r initializR}

knitr::opts_chunk$set( echo = FALSE, 
                       message = FALSE, 
                       warning = FALSE )

```

```{r pkgR}

library( tidyverse )
library( lubridate )
library( stringr )
library( broom )
library( gdata )

```

```{r impoRt}

# Read in each of the pertinent Excel spreadsheets.
otters.1 <- read.xls( xls = "data/RAW/2004 and 2005 N sea otter serology for Liz_JAN2014.xls", 
                      sheet = "Serology04-05", 
                      method = "csv", 
                      na.strings = c( "NA", "#DIV/0!", "" ), 
                      stringsAsFactors = FALSE ) %>% 
  filter( !is.na( Sea.Otter.ID ) ) # Remove the comment after the last line.

otters.2 <- read.xls( xls = "data/RAW/2004 and 2005 N sea otter serology for Liz_JAN2014.xls", 
                      sheet = "Morb Serology archived", 
                      method = "csv", 
                      na.strings = c( "NA", "#DIV/0!", "" ), 
                      stringsAsFactors = FALSE ) %>% 
  dplyr::select( -starts_with( "X" ) ) # File appends extra (empty) columns.

seals <- read.xls( xls = "data/RAW/PDV serology data for Ailsa_unedited.xlsx", 
                   sheet = "All species PDV only serology", 
                   method = "csv", 
                   na.strings = c( "NA", "#DIV/0!", "" ), 
                   stringsAsFactors = FALSE ) %>% 
  dplyr::select( -starts_with( "X" ) ) # Remove extra columns with comments.

```

```{r meRge}

# Combine the otter data and prettify names.
otters <- full_join( x = otters.1, 
                     y = otters.2, 
                     by = c( "Sea.Otter.ID" = "Sea.Otter.ID", 
                             "capture.date" = "Collection_Date", 
                             "Type_Source" = "Type_Source", 
                             "Sex" = "Sex", 
                             "Age.Class.Oct.06" = "Age.Class", 
                             "capture.location" = "Collec.location", 
                             "Ph.Dist" = "Ph.Dist" ) ) %>% 
  rename( ID = Sea.Otter.ID, 
          Date = capture.date, 
          Type = Type_Source, 
          Age.class = Age.Class.Oct.06, 
          Year = year, 
          Location = capture.location, 
          Area = area, 
          PDV = Ph.Dist, 
          pdv20 = X.20, 
          pdv30 = X.30, 
          CDV = CDV..OK. ) %>% 
  mutate( Species = "Southern sea otter", 
          ID = str_replace_all( string = ID, 
                                pattern = "^(?:\\s*)|(?:\\s*)$", 
                                replacement = "" ) )

# Prettify seal names.
seals <- seals %>% 
  rename( ID = AnimalID, 
          Date = CaptureDate, 
          Year = CaptureYear, 
          Location = CaptureSite, 
          Area = Region, 
          Region = BroadRegion, 
          Age_months = Age..mo., 
          Type = Disposition, 
          PDV_USA.2006 = PDV.Titre..USA2006., 
          PDV_NL.2002 = PDV.Titre..NL2002., 
          pdv24 = PDV.Result..24.................1...Pos..0...Neg., 
          pdv32 = PDV.Result..32.................1...Pos..0...Neg., 
          pdv64 = PDV.Result..64.................1...Pos..0...Neg. ) %>% 
  mutate( ID = str_replace_all( string = ID, 
                                pattern = "^(?:\\s*)|(?:\\s*)$", 
                                replacement = "" ) )

# Combine seal and otter data.
serology <- full_join( x = seals, 
                       y = otters, 
                       by = c( "ID", "Species", "Date", "Year", "Type", "Location", "Area", "Age.class", "Sex" ) )

```

```{r exploRe, include = FALSE, eval = FALSE}

with( serology, table( Species, useNA = "ifany" ) )
with( serology, table( Date, useNA = "ifany" ) )          # 3 NA; formats: %m/%d/%y, %m/%d/%Y, %Y-%m-%d, %m/%d/%Y - %m/%d/%Y, %b %Y, %b %y
with( serology, table( Year, useNA = "ifany" ) )          # 133 NA; 2001--2013
with( serology, table( Location, useNA = "ifany" ) )      # 7 NA
with( serology, table( Area, useNA = "ifany" ) )          # 230 NA
with( serology, table( Age, useNA = "ifany" ) )           # 749 NA; 2, 4-5, 7-12, 14-17, 20, 23-24, 26, 28, 38, 40, 45 months; P
with( serology, table( Age.class, useNA = "ifany" ) )     # 29 NA; A & Adult, J & Juvenile; P & Pup; 'Subadult' & 'Subadult '; U; YOY
with( serology, table( Sex, useNA = "ifany" ) )           # 214 NA; F & Female; M & Male; U & Unknown
with( serology, table( Type, useNA = "ifany" ) )          # Dead; live capture & Live capture & Live captured & Live-capture; Subsistence harvest
with( serology, table( pdv24, useNA = "ifany" ) )         # 222 NA; 0/1
with( serology, table( pdv32, useNA = "ifany" ) )         # 222 NA; 0/1
with( serology, table( pdv64, useNA = "ifany" ) )         # 222 NA; 0/1
with( serology, table( pdv20, useNA = "ifany" ) )         # 1346 NA; neg/pos
with( serology, table( pdv30, useNA = "ifany" ) )         # 1346 NA; neg/pos
with( serology, table( PDV_USA.2006, useNA = "ifany" ) )  # 728 NA; <#, <#T, > #, #, #T, unable to read T
with( serology, table( PDV_NL.2002, useNA = "ifany" ) )   # 789 NA; #
with( serology, table( PDV, useNA = "ifany" ) )           # 1204 NA; -, Neg, Neg (<=#), Neg (<#), Neg (#:#), Pos (#:#), Toxic (<#), Toxic (#:#), QNS, No sample
with( serology, table( CDV, useNA = "ifany" ) )           # 1292 NA; Neg (<#), Pos (#:#), Toxic (#:#), QNS, No sample
with( serology, table( DMV, useNA = "ifany" ) )           # 1409 NA; Neg (<#), Toxic (#:#), QNS
with( serology, table( PMV, useNA = "ifany" ) )           # 1409 NA; Neg (<#), QNS

```

```{r dateDealings}

# Parse dates.
# Replace "7/9/2010 - 8/9/2010" with "July 2010"
date.key <- c( "Jul 2010" = "7/9/2010 - 8/9/2010", "Sep 2004" = "Sept 04" )
serology$Date <- plyr::mapvalues( x = serology$Date, 
                                  from = date.key, 
                                  to = names( date.key ) )
# Unfortunately, this locks all Month-Year "dates" to the 1st of the month, and all Year-only "dates" to Jan 1st.
serology$lubriDate <- parse_date_time( x = serology$Date, 
                                       orders = c( "mdy", "Y", "Ymd", "mdY", "bY", "BY" ) )

# There are 4 Date-Year mismatches; I strongly suspect the year in "Year" is correct.
yrInds <- which( year( serology$lubriDate ) != serology$Year )           # Find them.
year( serology$lubriDate[ yrInds ] ) <- serology$Year[ yrInds ]          # Correct them.

# Now create separate columns for Year, Month, and Day (if available).
serology$Year <- year( serology$lubriDate )
serology$Month <- month( serology$lubriDate )
serology$Day <- mday( serology$lubriDate )

# BUT, some of those dates didn't actually have months or days (see comment above). We need to take care of that.
noDay <- which( !grepl( pattern = "\\/|-", x = serology$Date ) )        # Those without a day term are missing delimiters (i.e., / or -).
noMonth <- which( nchar( serology$Date ) == 4 )                         # Those without a month term are all limited to four characters.
# serology$Date[ noDay ]                                                # Check to be sure that these all DON'T have days.
# serology$Date[ noMonth ]                                              # Check to be sure that these all DON'T have months.
# serology$Date[ -noDay ]                                               # Check to be sure that these all DO have days.
# serology$Date[ -noMonth ]                                             # Check to be sure that these all DO have months.

# Now, re-train the month and day columns accordingly.
serology$Day[ noDay ] <- NA
serology$Month[ noMonth ] <- NA

```

```{r demographicDealings}

# Homogenize sex labels.
sex.key <- c( "F" = "Female", "M" = "Male", "U" = "Unknown" )
serology$Sex <- plyr::mapvalues( x = serology$Sex, 
                                 from = sex.key, 
                                 to = names( sex.key ) )

# Homogenize age labels.
age.key <- c( "A" = "Adult", "J" = "Juvenile", "P" = "Pup", "Subadult" = "Subadult ", "U" = "Unknown", "YOY" = "YOY" )
serology$Age.class <- plyr::mapvalues( x = serology$Age.class, 
                                       from = age.key, 
                                       to = names( age.key ) )

# 'Age' column contains both 'P' and 'Pup' values.
serology$Age <- plyr::mapvalues( x = serology$Age, 
                                 from = age.key, 
                                 to = names( age.key ) )

# with( serology, table( Age, Age_months, useNA = "ifany" ) )                # Check to be sure age categorizations are in agreement.

```

```{r diseaseDealings}

# These are the values that show up in the various titer columns (PDV_USA.2006, PDV_NL.2002, PDV, CDV, PMV, DMV)
# <#, <#T, > #, #, #T, unable to read T, -, Neg, Neg (<=#), Neg (<#), Neg (1:#), Pos (1:#), Toxic (<#), Toxic (1:#), QNS, No sample, NA
# I will deal with them each in the following ways with respect to titer value:
# NA <- unable to read T, -, QNS, No sample, NA, <#T, Toxic (<#), #T, Toxic (1:#)
# 0 <- <#, Neg, Neg (<=#), Neg (<#)
# # <- Neg (1:#), Pos (1:#), #, > #

# Create a function to coerce messy titer records into clean (numeric or NA) records by pattern matching.
tidyTiter <- function( .titer ){
  # where .titer is a [character] vector of messy titer records.
  
  ## Set patterns:
  # recognize as 0 titer
  ZT <- "(?:(?:<\\s*=?\\s*(\\d+\\.?\\d*))|[Nn]eg)"                        # all titers with the pattern "...<...#..."
  # recognize as some number
  NumT <- "(?:(?:1:)|(?:>\\s*))?(\\d+\\.?\\d*)"                           # all titers with the pattern "...1:#..." OR ">...#"
  # recognize as NA
  NAT <- "(?:[Uu]nable)|(?:-)|(?:[Qq][Nn][Ss])|(?:[Nn][Oo])|(?:[Nn][Aa])" # all titers with 'unable' OR '-' OR 'qns' OR 'na'
  # recognize toxic titers
  ToxT <- "(?:[Tt][Oo][Xx][Ii][Cc])|(?:(?<=\\d)(?:\\s*[Tt]))"             # all titers with pattern 'Toxic' OR '#...T'
  
  ## Find indices of each pattern and replace:
  # toxics
  ToxInd <- grepl( pattern = ToxT, x = .titer, perl = TRUE )  # Find!
  .titer[ ToxInd ] <- NA                                      # Replace!
  # zeros
  ZInd <- grepl( pattern = ZT, x = .titer )         # Find!
  .titer[ ZInd ] <- "0"                             # Replace!
  # numbers
  NumInd <- grepl( pattern = NumT, x = .titer )                                                                                 # Find!
  .titer[ NumInd ] <- gsub( pattern = paste( "\\D*", NumT, "\\D*", sep = "" ), replacement = "\\1", x = .titer[ NumInd ] )      # Replace!
  # NAs
  NAInd <- grepl( pattern = NAT, x = .titer )       # Find!
  .titer[ NAInd ] <- NA                             # Replace!
  
  as.numeric( .titer )                              # Numerize.
  
}

# # Check to be sure tidyTiter() is doing what you intend for it to do!
# with( serology, data.frame( tidyTiter( PDV_USA.2006 ), PDV_USA.2006 ) ) %>% distinct()
# with( serology, data.frame( tidyTiter( PDV_NL.2002 ), PDV_NL.2002 ) ) %>% distinct()
# with( serology, data.frame( tidyTiter( PDV ), PDV ) ) %>% distinct()
# with( serology, data.frame( tidyTiter( CDV ), CDV ) ) %>% distinct()
# with( serology, data.frame( tidyTiter( PMV ), PMV ) ) %>% distinct()
# with( serology, data.frame( tidyTiter( DMV ), DMV ) ) %>% distinct()

# Now tidy those titers!
serology$PDV_USA.2006_Titer <- tidyTiter( serology$PDV_USA.2006 )
serology$PDV_NL.2002_Titer <- tidyTiter( serology$PDV_NL.2002 )
serology$PDV_Titer <- tidyTiter( serology$PDV )
serology$CDV_Titer <- tidyTiter( serology$CDV )
serology$PMV_Titer <- tidyTiter( serology$PMV )
serology$DMV_Titer <- tidyTiter( serology$DMV )

# Create a function to check whether any titers in a series of titers for a given record exceed some cutoff.
titer.check <- function( .cutoff, .cols, .data ){
  # where .cutoff is some numeric critical minimum, .cols is a character vector of column names to check against (all .cols should be tidy titers!), and .data is the data.frame in which to search for .cols
  
  # First subset the .data and check to make sure .cols are numeric
  .data <- .data[ , .cols ]
  stopifnot( all( apply( X = .data, MARGIN = 2, FUN = is.numeric ) ) )

  # Now check across all .cols to see whether any EXCEED [>] the .cutoff. If all are NA, return NA. Otherwise, 1/0.
  hi.titer <- apply( X = .data, 
                     MARGIN = 1, 
                     FUN = function( .titers ) ifelse( test = all( is.na( .titers ) ), 
                                                       yes = NA, 
                                                       no = as.numeric( any( .titers > .cutoff, na.rm = TRUE ) ) ) )
  
  hi.titer
}

# Re-train PDV infection statuses.
pdv.cols <- c( "PDV_USA.2006_Titer", "PDV_NL.2002_Titer", "PDV_Titer" )
serology$pdv20 <- titer.check( 20, pdv.cols, serology )
serology$pdv30 <- titer.check( 30, pdv.cols, serology )
serology$pdv24 <- titer.check( 24, pdv.cols, serology )
serology$pdv32 <- titer.check( 32, pdv.cols, serology )
serology$pdv64 <- titer.check( 64, pdv.cols, serology )

# Create a function to check whether a messy titer indicates that the titer is 'toxic' (vectorized)
toxic.check <- function( .data, ... ){
  # where ... is a unquoted series of messy titer columns across which to check for toxic titer indicators in .data
  
  # Subset the data.
  .data <- select_( .data, .dots = lazyeval::lazy_dots( ... ) )

  # Define the regular expression pattern used to check for toxic titer indicators:
  # Looks for 'Toxic' (caseless) OR '#...T' (caseless) OR '...T'
  ToxT <- "(?:[Tt][Oo][Xx][Ii][Cc])|(?:(?<=\\d)(?:\\s*[Tt]))|(?:\\s+[T])"
  NAT <- "(?:-)|(?:[Qq][Nn][Ss])|(?:[Nn][Oo])|(?:[Nn][Aa])"     ##### SHOULD RETURN 'NA' if all( is.na( . ) ) == T | if all match some NAT pattern
  
  toxic.records <- apply( X = .data,                                                                         # within the subsetted data...
                          MARGIN = 2,                                                                        # look across rows...
                          FUN = function( .tt ){ 

                            ToxInd <- grepl( pattern = ToxT, x = .tt, perl = TRUE )                          # find locations of toxic indicators...
                            NAInd <- ( ( grepl( pattern = NAT, x = .tt, perl = TRUE ) ) | is.na( .tt ) )     # of NA values and NA indicators...
                            NoToxInd <- !( ToxInd | NAInd )                                                  # and of non-toxic titer records.
                            
                            .vv <- vector( mode = "logical", length = length( .tt ) )                        # allocate a new record.
                            .vv[ NAInd ] <- NA                                                               # replace NA records with 'NA'
                            .vv[ ToxInd ] <- TRUE                                                            # and toxic records with 'TRUE'.
                            .vv                                                                              # all others are 'FALSE'
                            } )
  
  toxic.records <- apply( X = toxic.records,                                                                 # within the new trinary (T/F/NA) data...
                          MARGIN = 1,                                                                        # look across columns...
                          FUN = function( .tt ){
                            if( any( .tt, na.rm = TRUE ) ){                                                  # if any observations for a record have a toxic indicator,
                              TRUE                                                                           # assign 'TRUE'
                            } else if( any( !.tt, na.rm = TRUE ) ){                                          # if not, and if there exists some other valid observation,
                              FALSE                                                                          # assign 'FALSE'
                            } else {                                                                         # otherwise,
                              NA                                                                             # assign 'NA'
                            }
                          } )
  
  as.numeric( toxic.records )                                                                                # return a binary [numeric] vector of the findings
  
}

# Check for toxic titers by disease.
serology$PDV_Toxic <- toxic.check( serology, PDV_USA.2006, PDV_NL.2002, PDV )
serology$CDV_Toxic <- toxic.check( serology, CDV )
serology$PMV_Toxic <- toxic.check( serology, PMV )
serology$DMV_Toxic <- toxic.check( serology, DMV )

```

```{r deDuplicatoR}

# duplicate entries: Yun04-15, Yun04-19, A198, A240, #35, 125PG, AT1
# recaptures: A00414, A00427, A00428
# likely different animals: Bog1, SO9829, SO0128

# # Review IDs and identify those that occur multiply.
# ids <- with( serology, data.frame( table( ID, useNA = "ifany" ) ) )
# dupIDs <- as.character( ids[ which( ids$Freq != 1 ), ]$ID )
# dups <- serology[ which( serology$ID %in% dupIDs ), ]

# After review with EVW, the duplicate cases are thought to fall into one of the following categories:
trueDups <- c( "#35", "125PG", "A198", "A240", "AT1", "Yun04-15", "Yun04-19" )                         # true duplicates----------remove non-unique cases
recaps <- c( "A00414", "A00427", "A00428" )                                                            # recaptures---------------preserve, but indicate recapture
dblIds <- c( "Bog1", "SO0128", "SO9829" )                                                              # doubly-assigned IDs------re-assign IDs

# # Examine duplicate entries to preserve unique data among all records.
# dups[ which( dups$ID == trueDups[ 1 ] ), ] # #35--------2 records; 1 record includes value in PDV_NL.2002 not in other
# dups[ which( dups$ID == trueDups[ 2 ] ), ] # 125PG------2 records; identical
# dups[ which( dups$ID == trueDups[ 3 ] ), ] # A198-------2 records; 1 record includes value in PDV_NL.2002 not in other
# dups[ which( dups$ID == trueDups[ 4 ] ), ] # A240-------2 records; 1 record includes value in PDV_NL.2002 not in other
# dups[ which( dups$ID == trueDups[ 5 ] ), ] # AT1--------2 records; different values in PDV_USA.2006                                   <-------!!!
# dups[ which( dups$ID == trueDups[ 6 ] ), ] # Yun04-15---2 records; 1 record includes value in PDV_NL.2002 not in other
# dups[ which( dups$ID == trueDups[ 7 ] ), ] # Yun04-19---2 records; 1 record includes value in PDV_NL.2002 not in other

# # Examine recapture entires (just to be safe)
# dups[ which( dups$ID == recaps[ 1 ] ), ]  # A00414------2 records; 4 & 8 months (10/2003 & 2/2004)
# dups[ which( dups$ID == recaps[ 2 ] ), ]  # A00427------2 records; 4 & 8 months (11/2003 & 2/2004)
# dups[ which( dups$ID == recaps[ 3 ] ), ]  # A00428------2 records; 4 & 8 months (11/2003 & 2/2004)

# # Examine doubly-assigned ID cases
# dups[ which( dups$ID == dblIds[ 1 ] ), ]  # Bog1--------2 records; 5 years later, 1 month younger
# dups[ which( dups$ID == dblIds[ 2 ] ), ]  # SO0128------2 records; 4 years later
# dups[ which( dups$ID == dblIds[ 3 ] ), ]  # SO9829------3 records; 1998, 2001, 2005

# Create a function to reconcile duplicate records.
deDuplicator <- function( .data, .col, .ids, .type = c( "duplicate", "recurrence", "double" ), recur.col = "Recapture", seq.col = "Date" ){
  # where .col is the quoted name of the identification column in .data through which to search for the individuals given in .id (a character vector)
  # .type is the type of reconciliation sought:
  #### if "duplicate", all rows with .ids are condensed into 1
  #### if "recurrence", all rows with .ids are kept, but the "Recapture" column receives a '1' in later instances
  #### if "double", row .ids are reassigned to be unique
  
  .type <- match.arg( .type, choices = c( "duplicate", "recurrence", "double" ) )

  if( identical( .type, "duplicate" ) ){                                                                                      # If the duplication is a true duplication (error):
    for( ii in .ids ){                                                                                                        # For each duplicated id,
      idInds <- which( .data[ , .col ] %in% ii )                                                                              # determine the row ## in which it occurs.
      numNAs <- apply( .data[ idInds, ], MARGIN = 1, FUN = function( .rr ) sum( is.na( .rr ) ) )                              # Count the number of missing observations for each record.
      missingMore <- idInds[ -which.min( numNAs ) ]                                                                           # Figure out which are missing a larger chunk of data,
      .data <- .data[ -missingMore, ]                                                                                         # and remove those records from the data.
    }
  } else if( identical( .type, "recurrence" ) ){                                                                              # If the duplication represents a recurrence:
    for( ii in .ids ){                                                                                                        # For each duplicated id,
      idInds <- which( .data[ , .col ] %in% ii )                                                                              # determine the row ## in which it occurs.
      firstInd <- which.min( .data[ idInds, seq.col ] )                                                                       # Look in seq.col to determine which record is earliest,
      .data[ idInds[ -firstInd ], recur.col ] <- 1                                                                            # and assign all other records a '1' in the recur.col
    }
  } else if( identical( .type, "double" ) ){                                                                                  # If the duplication represents a double-assignation of an ID:
    for( ii in .ids ){                                                                                                        # For each duplicated id,
      idInds <- which( .data[ , .col ] %in% ii )                                                                              # determine the row ## in which it occurs
      idInds <- idInds[ order( .data[ idInds, seq.col ] ) ]                                                                   # and sort the indices by order of seq.col.
      .data[ idInds, .col ] <- paste( .data[ idInds, .col ], letters[ seq_along( idInds ) ], sep = "_" )                      # Append differentiators to the ids by order of seq.col.
    }
  }
  
  .data                                                                                                                       # Return the .data.
  
}

serology$Recapture <- 0    # Create a new column (used by deDuplicator if .type=="recurrence") to indicate recaptures.

# deDuplicate!
serology <- deDuplicator( serology, "ID", trueDups, .type = "duplicate" )                                                   # Remove duplicate entries.
serology <- deDuplicator( serology, "ID", recaps, .type = "recurrence", recur.col = "Recapture", seq.col = "lubriDate" )    # Indicate recaptures.
serology <- deDuplicator( serology, "ID", dblIds, .type = "double", seq.col = "lubriDate" )                                 # Clarify doubly-used identifiers.

# # Check:
# ids <- with( serology, data.frame( table( ID, useNA = "ifany" ) ) )
# dupIDs <- as.character( ids[ which( ids$Freq != 1 ), ]$ID )
# dups <- serology[ which( serology$ID %in% dupIDs ), ]                # The only duplicates are (correctly-indicated) recaptures...
# nrow( serology )                                                     # There are now 7 fewer entries...
# sum( serology$Recapture )                                            # Only 3 recapture events.

```

###**N O T E S** {#notes}

48 fur seals sampled on St. Paul Island, AK between 7/9/2010 and 8/9/2010 were collectively assigned a July sampling date.

-----

These are the values that show up in the various titer columns (`PDV_USA.2006`, `PDV_NL.2002`, `PDV`, `CDV`, `PMV`, `DMV`)

`<#`, `<#T`, `> #`, `#`, `#T`, `unable to read T`, `-`, `Neg`, `Neg (<=#)`, `Neg (<#)`, `Neg (1:#)`, `Pos (1:#)`, `Toxic (<#)`, `Toxic (1:#)`, `QNS`, `No sample`, `NA`

I will deal with them each in the following ways with respect to titer value:

* `NA` `<-` `unable to read T`, `-`, `QNS`, `No sample`, `NA`, `<#T`, `Toxic (<#)`, `Toxic (1:#)`
* `0` `<-` `<#`, `Neg`, `Neg (<=#)`, `Neg (<#)`
* `#` `<-` `Neg (1:#)`, `Pos (1:#)`, `#`, `> #`

-----

I deDuplicated the following individuals:

* True duplicates: `#35`, `125PG`, `A198`, `A240`, `AT1`, `Yun04-15`, `Yun04-19`
* Recaptures: `A00414`, `A00427`, `A00428`
* Doubly-assigned IDs: `Bog1`, `SO0128`, `SO9829`

Using the following methods:

* True duplicates: removed cases (_i.e._, rows) with more NA values
* Recaptures: Preserved all rows; indicated recurrences with a `1` in `Recapture` column
* Doubly-assigned IDs: appended `a, b, c, ...` to each ID